Death By Dropdown?

### 2025-04-08 conference-materials/2025_shiny-conf/slides.qmd
Adds SKIM theme to title slide
- Introduces a new background image for the title slide in the presentation with SKIM theme.

TODO: Update title and thank you slides with css vs current background images

---
title: "Death By Dropdown?"
subtitle: "A Developer's Guide To Building Dashboards That Won't Fry Your Client's Brain"
author: "Milena Eickhoff & Jeremy Winget, PhD"
format: 
  revealjs:
    theme: simple
    slide-number: false
    footer: "ShinyConf 2025 | Death By Dropdown?"
    incremental: true
    transition: slide
    background-transition: fade
    highlight-style: github
    code-block-background: true
---

>>>>

---
title: "Death By Dropdown?"
subtitle: "A Developer's Guide To Building Dashboards That Won't Fry Your Client's Brain"
author: "Milena Eickhoff & Jeremy Winget, PhD"
format: 
  revealjs:
    title-slide-attributes:
      data-background-image: "img/title.png"
      data-background-size: "100% 100%"
    theme: simple
    slide-number: false
    footer: "ShinyConf 2025 | Death By Dropdown?"
    incremental: true
    transition: slide
    background-transition: fade
    highlight-style: github
    code-block-background: true
---
